Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/model.tex
foaosdfs

We have so far focused on single-object, single-operation
availability. This is standard in the distributed systems literature
(e.g., linearizable, and regular register models all concern
single objects~\cite{herlihy-art}), yet the database literature
largely focuses on transactions: groups of multiple operations over
multiple objects. Accordingly, by itself, replica availability is
insufficient to describe availability guarantees for
transactions. Additionally, given the choice of \textit{commit} and
\textit{abort} responses---which signal transaction success or failure
to a client---we must carefully define transactional availability.

>>>>

We have so far focused on single-object, single-operation
availability. This is standard in the distributed systems literature
(e.g., linearizable and regular register models all concern single
objects~\cite{herlihy-art}), yet the database literature largely
focuses on transactions: groups of multiple operations over multiple
objects. Accordingly, by itself, replica availability is insufficient
to describe availability guarantees for transactions. Additionally,
given the choice of \textit{commit} and \textit{abort}
responses---which signal transaction success or failure to a
client---we must carefully define transactional availability.
